Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-22 main.tex
Some work on the discussion.

\section{Results}
%
The coefficient estimates for a single-level logistic regression at
6~\unit{\kph} with gain $g=10$ are shown in
Table~\ref{table:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs-6}.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $g=10$. Multiplicative change in
    odds of predictor variables at 6 \unit{\kilo\meter\per\hour} and gain
    $g=10$ based on frequentist single-level logistic regression.}
  \label{table:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse & 1.69 & 0.27 & 0.00 & 5.40 & 3.18 & 9.16 \\
    Perturbation order & -0.77 & 0.22 & 0.00 & 0.46 & 0.30 & 0.72 \\
    Balance assist state & -0.64 & 0.27 & 0.02 & 0.53 & 0.31 & 0.89 \\
    Roll angle & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance-assist on $\times$ roll angle & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance-assist on $\times$ steer angle & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance-assist on $\times$ angular impulse & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance-assist on $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

The coefficient estimates for a single-level logistic regression at
10~\si{\kilo\meter\per\hour} with gain $g=8$ are shown in Table
\ref{table:freq-coefs}. The angular impulse and perturbation order are
statistically significant predictors. Larger angular impulse increases the
probability to fall and enduring more perturbations decreases the probability
to fall. The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs}.

\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    10~\unit{\kilo\meter\per\hour} and gain $g=8$.  Multiplicative change in
    odds of predictor variables at 10 \unit{\kilo\meter\per\hour} based on
    frequentist single-level logistic regression. and 5\% confidence intervals
  of MCiO.}
  \label{table:freq-coefs}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept                                     & -0.24 & 0.16 & 0.13 & 0.78 & 0.57 & 1.07 \\
    Angular impulse                               & 2.39  & 0.29 & 0.00 & 10.92 & 6.23 & 19.13 \\
    Perturbation order                            & -1.16 & 0.21 & 0.00 & 0.31 & 0.21 & 0.48 \\
    Balance-assist on                             & -0.44 & 0.24 & 0.07 & 0.64 & 0.40 & 1.03 \\
    Roll angle                                    & 0.27  & 0.22 & 0.22 & 1.31 & 0.85 & 2.04 \\
    Steer angle                                   & -0.37 & 0.24 & 0.12 & 0.69 & 0.43 & 1.10 \\
    Balance-assist on $\times$ roll angle         & -0.61 & 0.34 & 0.08 & 0.54 & 0.28 & 1.07 \\
    Balance-assist on $\times$ steer angle        & 0.56  & 0.35 & 0.11 & 1.76 & 0.88 & 3.50 \\
    Balance-assist on $\times$ angular impulse    & 0.46  & 0.44 & 0.29 & 1.59 & 0.68 & 3.74 \\
    Balance-assist on $\times$ perturbation order & -0.37 & 0.32 & 0.25 & 0.69 & 0.37 & 1.30 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\section{Discussion}
%

It is important to understand the relationship between probability and odds to
relate Figure~\ref{fig:probability} and Table~\ref{tab:freq-coeffs-6}.  How
much the probability that a fall changes depends on the values of all predictor
variables and we visualize only one view into the results here. If the odds
that a perturbation results in a fall are a 1000:1, turning on the
balance-assist system reduces the odds to 500:1. However, the probability that
a fall occurs is only reduced from $0.999$ to $0.998$. On the other hand, if
the odds that a fall will occur are smaller, halving the odds has a larger
influence on the fall probability.For example, if the odds that a fall occurs
is two, halving it to one reduces the probability from $0.66$ to $0.50$. This
clearly shown in the behavior in Figure~\ref{fig:probablity} with the behavior
at high standard deviations.

>>>>

\section{Results}
%
The coefficient estimates for a single-level logistic regression at
6~\unit{\kph} with gain $g=10$ are shown in
Table~\ref{tab:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{tab:freq-coefs-6}.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $g=10$. Multiplicative change in
    odds of predictor variables at 6 \unit{\kilo\meter\per\hour} and gain
    $g=10$ based on frequentist single-level logistic regression.}
  \label{tab:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse & 1.69 & 0.27 & 0.00 & 5.40 & 3.18 & 9.16 \\
    Perturbation order & -0.77 & 0.22 & 0.00 & 0.46 & 0.30 & 0.72 \\
    Balance assist state & -0.64 & 0.27 & 0.02 & 0.53 & 0.31 & 0.89 \\
    Roll angle & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance-assist on $\times$ roll angle & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance-assist on $\times$ steer angle & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance-assist on $\times$ angular impulse & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance-assist on $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

The coefficient estimates for a single-level logistic regression at
10~\si{\kilo\meter\per\hour} with gain $g=8$ are shown in Table
\ref{tab:freq-coefs-10}. The angular impulse and perturbation order are
statistically significant predictors. Larger angular impulse increases the
probability to fall and enduring more perturbations decreases the probability
to fall.

\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    10~\unit{\kilo\meter\per\hour} and gain $g=8$.  Multiplicative change in
    odds of predictor variables at 10 \unit{\kilo\meter\per\hour} based on
    frequentist single-level logistic regression. and 5\% confidence intervals
  of MCiO.}
  \label{tab:freq-coefs-10}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept                                     & -0.24 & 0.16 & 0.13 & 0.78 & 0.57 & 1.07 \\
    Angular impulse                               & 2.39  & 0.29 & 0.00 & 10.92 & 6.23 & 19.13 \\
    Perturbation order                            & -1.16 & 0.21 & 0.00 & 0.31 & 0.21 & 0.48 \\
    Balance-assist on                             & -0.44 & 0.24 & 0.07 & 0.64 & 0.40 & 1.03 \\
    Roll angle                                    & 0.27  & 0.22 & 0.22 & 1.31 & 0.85 & 2.04 \\
    Steer angle                                   & -0.37 & 0.24 & 0.12 & 0.69 & 0.43 & 1.10 \\
    Balance-assist on $\times$ roll angle         & -0.61 & 0.34 & 0.08 & 0.54 & 0.28 & 1.07 \\
    Balance-assist on $\times$ steer angle        & 0.56  & 0.35 & 0.11 & 1.76 & 0.88 & 3.50 \\
    Balance-assist on $\times$ angular impulse    & 0.46  & 0.44 & 0.29 & 1.59 & 0.68 & 3.74 \\
    Balance-assist on $\times$ perturbation order & -0.37 & 0.32 & 0.25 & 0.69 & 0.37 & 1.30 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\section{Discussion}
%
Starting with Figure~\ref{fig:probability} and Table~\ref{tab:freq-coeffs-6}.

To interpret the results in Tables~\ref{tab:freq-coeffs-6} and
\ref{tab:freq-coeffs-10}
it is important to understand the relationship between probability and odds.
The probability that a fall occurs depends on the values of all the indepedent
variables and but we can visualize one view into the results in
Figure~\ref{fig:probability}. The estimate in Table~\ref{tab-freq-coeffs-6}
shows that if the odds that the balance assist system halves the odds that a
perturbation results in a fall. For example, if the odds are a 1000:1,
turning on the balance-assist system reduces the odds to 500:1. However, the
probability that
a fall occurs is only reduced from $0.999$ to $0.998$. If
the odds that a fall will occur are smaller, halving the odds has a larger
influence on the fall probability.For example, if the odds that a fall occurs
is two, halving it to one reduces the probability from $0.66$ to $0.50$. This
clearly shown in the behavior in Figure~\ref{fig:probablity} with the behavior
at high standard deviations.
